Distributed Decision Making for Dynamic Formation of Web Services Communities

### 2015-01-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{table}[ht]
\caption{Utility gain of web services after making collaborative groups based on DDM algorithm with different $r$ rates} % title of Table
\centering % used for centering table
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c|c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
Search Rate $r$ & Utility Gain Value & Utility Gain Ratio \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
r=0.05 & 176.1499 & 6.9690 \\
r=0.07 & 174.6541 & 6.9182 \\
r=0.10 & 159.9462 & 6.2834 \\
r=0.20 & 136.0768 & 5.1032 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:valueandgain} % is used to refer this table in the text
\end{table}

>>>>

\begin{table}[ht]
\caption{Utility gain of web services after making collaborative groups based on DDM algorithm with different $r$ rates} % title of Table
\centering % used for centering table
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c|c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
Search Rate $r$ & Utility Gain Value & Utility Gain Ratio \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
r=0.20 & 176.1499 & 6.9690 \\
r=0.10 & 174.6541 & 6.9182 \\
r=0.07 & 159.9462 & 6.2834 \\
r=0.05 & 136.0768 & 5.1032 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:valueandgain} % is used to refer this table in the text
\end{table}
